---
title: "Formative Assessment 7"
author: "Lindsy Rossel C. Masicat"
date: "2024-02-29"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. In Example 16.3 with ðœ† = 4 per minute, use R to obtain:
+ (a) P(T â‰¤ 0.25) = P(time between submissions is at most 15 seconds);

```{r 1.a}
ave = 4
pexp(0.25, ave)
```

+ (b) P(T > 0.5) = P(time between submissions is greater than 30 seconds);
```{r 1.b}
1 - pexp(0.5, ave)
```

+ (c) P(0.25 < T < 1) = P(time between submissions is between 15 seconds
and 1 minute).
```{r 1.c}
pexp(1, ave) - pexp(0.25, ave)
```


3. The average rate of job submissions in a computer center is 2 per minute. If
it can be assumed that the number of submissions per minute has a Poisson
distribution, calculate the probability that:
+ (a) more than two jobs will arrive in a minute;
```{r 3.a}
ave <- 2
morethan2 <- 1 - sum(dpois(0:2, ave))
print(paste("Probability of more than two jobs arriving in a minute:", morethan2))
```
+ (b) at least 30 seconds will elapse between any two jobs;
<br>P(T â‰¥ 0.5)= P(time between submissions is at least 30 seconds)
```{r 3.b}
1 - pexp(0.5, ave)
```
+ (c) less than 30 seconds will elapse between jobs;
<br>P(T < 0.5)= P(time between submissions is less than 30 seconds)
```{r 3.c}
pexp(0.5, ave)
```
+ (d) a job will arrive in the next 30 seconds, if no jobs have arrived in the last
30 seconds.
<br>P(0.5 â‰¤ T â‰¤ 1)= P(time between submissions is in between of 30 and 60 seconds)

```{r 3.d}
pexp(1, ave) - pexp(0.5, ave)
```


7. A website receives an average of 15 visits per hour, which arrive following a
Poisson distribution.
+ (a) Calculate the probability that at least 10 minutes will elapse without a
visit.
<br> 10 minutes is 0.16666667 of an hour 
<br>P(0.16666667 â‰¤ T )= P(time between visits is at least 10 minutes)
```{r 7.a}
ave = 15
pexp(0.16666667, ave)
```
+ (b) What is the probability that in any hour, there will be less than eight visits?
<br>P(X < 8 )= P(less than eight visits)

```{r 7.b}
ppois(7, ave)
```
+ (c) Suppose that 15 minutes have elapsed since the last visit, what is the probability that a visit will occur in the next 15 minutes.
<br>P(0.25 < T â‰¤ 0.5)= P(time between visits is between 15 and 30 minutes)
```{r 7.c}
 pexp(0.5, ave) - pexp(0.25, ave)
```
+ (d) Calculate the top quartile, and explain what it means
```{r 7.d}
qpois(0.75, ave)
```

